How Kids Code and How We Know:\\An Exploratory Study on the Scratch Repository

### 2016-04-22 Paper/paper.tex
Added info on introduction

Several studies have shown that block-based languages are powerful as a tool for teaching programming~\cite{meerbaum-salant_learning_2010, b._moskal_evaluating_2005,cooper_teaching_2003}. \todo{Fenia, do you have some work on Research on programming habits}

Recent work has focused on \emph{code smells} within Scratch programs, parts of a program that are not designed in the best possible way. \todo{add dr. scratch papers here} Ar recent controlled experiment found that long scripts and duplication decreases a novice programmer's ability to understand and modify Scratch programs \todo{cite}.

The goal of this paper is to obtain a deep understanding of how people program in Scratch and to analyze the characteristics of Scratch programs. Moreover, knowing that bad programming habits and code smells can be harmful, we also want to explore whether they are common. Specifically, the research questions that we are trying to answer are:

@@

Our study is based on data from the Scratch project repository. By scraping the list of recent projects \footnote{\url{https://scratch.mit.edu/explore/projects/all/}}, we have obtained \nPrograms~public Scratch projects and performed analysis on them.

>>>>

Several studies have shown that block-based languages are powerful as a tool for teaching programming~\cite{meerbaum-salant_learning_2010, b._moskal_evaluating_2005,cooper_teaching_2003}. Research works involving static analysis of Scratch programs \cite{Maloney_2008} \cite{moreno_automatic_2014} have evaluated the use of various programming concepts in 536 and 100 Scratch projects respectively. Recent work has focused on bad programming practices and habits within Scratch programs \cite{Meerbaum_habits_2011}, and automated quality assessment tools have been proposed for identifying code smells and bad programming practices \cite{boe_hairball:_2013}\cite{moreno_automatic_2014}. Ar recent controlled experiment found that long scripts and duplication decreases a novice programmer's ability to understand and modify Scratch programs \todo{cite}.

The goal of this paper is to obtain a deep understanding of how people program in Scratch, to analyze the characteristics of Scratch programs, and to quantitatively evaluate the use of programming abstractions and concepts. Moreover, knowing that bad programming habits and code smells can be harmful, we also want to explore whether they are common. Specifically, the research questions that we are trying to answer are:

@@

Our study is based on data from the Scratch project repository. By scraping the list of recent projects \footnote{\url{https://scratch.mit.edu/explore/projects/all/}}, we have obtained \nPrograms~public Scratch projects and performed analysis on them. To the best of our knowledge, this is the first large-scale exploratory study on Scratch projects.
